Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-24 background_and_systematic.tex
minor update

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. \blue{An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well and to keep consistency with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data. In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

>>>>

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. \blue{An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well \blue{and is consistent with} Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data. In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

### 2011-02-24 theory.tex
minor update

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four momentum of the proton; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference in the
change of the fraction of the nucleon's longitudinal momentum carried by the
active quark at the start and end of the process, written as the skewness
variable $\xi$; and the square $-Q^2=q^2$ of the \blue{of the four-momentum of the virtual photon that mediates the lepton-proton scattering process.} In the Bjorken limit of $Q^2\rightarrow\infty$ with
fixed $t$, $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p.q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
against $x_{\textrm{B}}$ because there is no consensus on an experimentally
observable representation of $\xi$.

>>>>

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four-momentum of the proton; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference in the
change of the fraction of the nucleon's longitudinal momentum carried by the
active quark at the start and end of the process, written as the skewness
variable $\xi$; and the square $-Q^2=q^2$ of the \blue{of the four-momentum of the virtual photon that mediates the lepton-proton scattering process.} In the Bjorken limit of $Q^2\rightarrow\infty$ with
fixed $t$, $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p.q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
against $x_{\textrm{B}}$ because there is no consensus on an experimentally
observable representation of $\xi$.
